---
title: "Figure 12"
output: pdf_document
---

```{r, echo=F, message=F}

u.t.subset <- data$num_urls[data$is_fake_news==T]
u.f.subset <- data$num_urls[data$is_fake_news==F]

ks <- ks.test(u.t.subset, u.f.subset)
ks.p <- formatC(ks$p.value, format='e', digits=2)

t <- t.test(u.t.subset, u.f.subset)
t.p <- formatC(t$p.value, format='e', digits=2)

caption.t <- paste('T-test p-value:', t.p)
caption.ks <- paste('KS-test p-value:', ks.p)
```

```{r, echo=F, message=F}
result <- factor(data$is_fake_news, levels = c("TRUE", "FALSE"))

ggplot(data, aes(x=num_urls, group=result, fill=result)) + geom_histogram(aes(y=..density..), position="dodge") + scale_y_continuous(labels=function(x) paste0(x/10)) + scale_color_manual(values = c("#df6066", "#80bab4"), labels = c("Fake News","Other")) + scale_fill_manual(values = c( "#df6066", "#80bab4"), labels = c("Fake News","Other")) + labs(y="Density", caption=paste(caption.t, caption.ks)) + theme(legend.title=element_blank(), plot.caption=element_text(hjust=0.5)) + ggtitle("Distribution of Number of URLs Per Tweet")
```

## Process of Figure 12 Replication

In the original paper, Figure 12 captures the distribution of the portion of tweets with different 
amounts of URLs embedded within. A histogram was used to represent the distributions for tweets 
classified as 'fake news,' and not, side-by-side. 

Replicating this figure proved to be complicated. Note that the replicated figure features the 
exact same distribution bars/curve as in the original figure. That is, the relationships between
the portions (for any given number of URLs) match the relationships in the original chart.

There are, however, certain differences. Notably, the x-axis is scaled differently (despite the 
bars painting an identical picture). This is likely because the original creators factored the 
num_urls variable into a discrete one. Here, programming errors mandated that num_urls be
treated as a continuous one (hence the extraneous x-axis ticks). 

Additionally, the scale on the y-axis is slightly shifted (upwards) in the replicated figure, 
which initially suggests that mis-replication. Instead, the original authors must have used some
unique function to yield the "normalized percent of tweets" that was not available here. Note 
that all normalization functions in geom_histogram() have the same intent: to produce a density 
plot where the sum area under the bars of one distribution is 1. For instance, the red (fake-news) 
bars in the original figure indeed sum to 1. While that exact density-calculating function was
not used, this property is preserved in the new figure. Also, the pattern made by the bars in 
the original figure is also preserved, and so are the conclusions that can be drawn from it. So,
while the process of replication differed, the results are nigh-identical and statistically sound. 

Note that differences are statistically significant at alpha = 0.05, as expected. 
