---
title: "Figure 7"
author: "Juan Solorio"
date: "2/23/2020"
output: html_document
---

```{r, load-&-libraries, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = F)
#library(tidyverse)
#library(ggpubr)

#data <- read.csv("../Data/electionday_tweets_clean.csv")
tweets <- data[,]
tweets$FakeNewsLabel <- ifelse(tweets$is_fake_news == TRUE, 'fake news', 'other')

```



```{r, calc-pval, echo=FALSE, message=FALSE, warning=FALSE}
followes.ks <- ks.test(tweets$user_followers_count[tweets$is_fake_news==T],tweets$user_followers_count[tweets$is_fake_news==F])

pval.followes.ks <- formatC(followes.ks$p.value, format = 'e', digits = 2)

followes.t <- t.test(tweets$user_followers_count[tweets$is_fake_news==T],tweets$user_followers_count[tweets$is_fake_news==F])

pval.followes.t <- formatC(followes.t$p.value, format = 'e', digits = 2)

```



```{r, figure7, fig.cap = 'Replication of figure 7, displaying density distributions of the number of followers that the accounts generating viral tweets. Showing statistical significance in the difference between the distributions.', warning=FALSE}

basicPlot <- ggplot(data = tweets, aes(x = user_followers_count, fill = FakeNewsLabel ,
  color= FakeNewsLabel)) +
  geom_density(alpha = .5) +
  ggtitle(label = 'Distribution of followers') + 
  theme(plot.title = element_text(size = 9, face = 'bold'),
        legend.title = element_blank())

basicPlot + scale_x_continuous(name = 'number of followers (log10)',trans = 'log10',
                     breaks = c(1e+02, 1e+04, 1e+06, 1e+08),
                     labels = c('2','4','6','8')) + annotate("text", x = 1e+03:1e+03, y = c(.4,.5), label = c(paste(' T-test p-value:',pval.followes.t),paste(' KS test p-value:',pval.followes.ks)),size=3)
```



## Process of Figure 7 Replication

In replicating Figure 7, which displayed a density distribution of followers between accounts labeled as Fake News or Other from the currated data source, there were a few data manipulation that were needed to replicate the figure through the ggplot2 library in R. Moreover, the original purpose for the figure is to graphically show statistically significant difference between the distributions of labeled accounts.

The first, the data was read from the "Electionday_tweets_clean.csv" data file provided by [@TweetsOriginal] research and passed into the *ggplot* and *aes* functions. Through the aes function, the *x* aes value given the **user_followers_count** and the *fill* value (which splits the data by category) was passed a new engineered column **FakeNewsLabel**, which provided the appropiate labels of "Fake News" and "Other" from the boolean values given by the **is_fake_news** column. Next the geom_density function is added the ggplot code, defining the type of graph that will be created. To the code we then have to make a log transformation to the x-axis, as the data is too widely distributed for the number of followers for the various accounts. The log transform is accomplished by the *scale_x_continuous(trans = 'log10')* command. This provides with the basic plot that replicates the output similar to that of the original Figure 7 [@TweetsOriginal].

Additional aesthetic aspects were added to our replication, such as the addition of p-values for both a *Welch T-test* and a *Kolmogorov-Smirnov test* into the figure, calculated through the R functions *t.test* and *ks.test*. Both test show a p-value of statistical significance for the distribution of followers between "Fake News" and "Other" accounts.
